---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753LW)
```

# Introduction

The MATH4753LW package contains functions utilized in the MATH4753 course at the University of Oklahoma. This vignette provides examples of how to use the functions in the package.

# mysq function

The mysq function calculates the square of a number. For example, the square of 3 is 9.

```{r}
mysq(3)
```

mysq() can also square a vector of numbers. For example, the squares of 1, 2, and 3 are 1, 4, and 9, respectively.

```{r}
mysq(1:3)
```

mysq() can also square a matrix of numbers.

```{r}
mysq(matrix(1:9, nrow = 3))
```

# getmode function

The mode function calculates the mode of a vector of numbers. For example, the mode of 1, 2, 2, 3, and 4 is 2.

```{r}
getmode(c(1, 2, 2, 3, 4))
```

# mysample function

The mysample function generates random samples of n numbers from 1-10 with replacement, for a specified number of iterations, and shows a barplot with the frequency of each number for each iteration. For example, the following code generates 10 random samples of 10 numbers from 1-10 with replacement. (Default iterations are 10 with .5 seconds between each barplot generation)


```{r}
mysample(10)
```

You can also change the number of iterations and time between each iteration.

```{r}
mysample(10, 5, 1)
```

# mybin function

The mybin function creates a histogram of a vector of numbers with a specified number of bins. For example, the following code creates a histogram of 100 random numbers from a normal distribution with 10 bins.

```{r}
